---
title: "DVCR Forum with MCRs (April 2024)"
subtitle: "Summary of Responses to RDS Survey: Complete Report"
#author: "Jen Beaudry"
#date: "11/07/2024"
output: pdf_document
editor_options: 
  chunk_output_type: console
header-includes:
  - \usepackage{caption}
  - \usepackage{titling}
    \setlength{\droptitle}{-2cm} # removes some of the white space above title
  - \pretitle{\begin{center}
    \includegraphics[width=1.5in, height=1.5in]{flinders-university-horizontal-master.png}\LARGE\\} # adds logo
  - \posttitle{\end{center}}
  - \usepackage{fancyhdr}
  - \fancypagestyle{plain}{\pagestyle{fancy}} # sets the footer on page 1
  - \pagestyle{fancy} # sets the footer on page 2 and beyond
  - \fancyhf{} # clears existing header & footer
  - \renewcommand{\headrulewidth}{0pt} # removes the line from the header
#  - \fancyfoot[L]{Jen Beaudry} # my name in footer
  - \fancyfoot[R]{\thepage} # page number in foooter
---

```{r setup, include=FALSE}

### NOTE: USE THIS FOR THE FULL REPORT ###

knitr::opts_chunk$set(echo = FALSE,
                      include = TRUE, 
                      eval = TRUE)

# REMEMBER: Until you figure out parameterized reports, you'll have to manually 
  # select which chunks to run and will need to delete the 'empty pages' that 
  # aren't included in Rob's report

```

```{r library, include=FALSE}

library(here)
library(tidyverse)
library(kableExtra)
library(RColorBrewer)

```

```{r functions, include=FALSE}

styler_pdf <- function(dat) {
  dat %>%
     kable_styling(full_width = F, 
                latex_options = c("striped", "HOLD_position"))
}

source(here("..", "functions", "ratings_summary.R"))

```

```{r load data, include=FALSE}

df <- read_csv(here::here("data", "mcr_forum_processed.csv"), lazy = FALSE)

attendees <- as.integer(29)

```

We asked our attendees five questions. Two were about the forum, one was about
the training and development offerings that they would like to see, one was about 
how they want us to communicate opportunities to them, and one was an 
open-ended question givingthem a chance to tell us anything else they wanted us to know. 

Of the `r attendees` mid-career researchers who attended this session, `r nrow(df)` 
completed the survey. The responses might not be reflective of the attitudes of 
all attendees because of the low response rate (`r round((nrow(df)/attendees*100),2)`%).   

\captionsetup[table]{labelformat=empty}

## Feedback about today's DVC(R) forum with MCRs
What did you think about today's forum?

```{r table for feedback}

# use for complete report and report for DVCR

# put relevant data in a tibble
feedback <- df %>% 
  dplyr::select(c(id, feedback)) %>% 
  filter(!feedback == "NA") %>%  # remove the NA values
  mutate(responses = 1:n()) %>% 
  relocate(responses, .after = id)

# get the relevant ns for the header
total_n <- length(unique(df$id))
resp_n <- length(unique(feedback$id))
ns <- c(total_n, resp_n) 

feedback <- feedback %>% 
  dplyr::select(c(id, feedback))

knitr::kable (
  feedback,
  booktabs = T,
  linesep = "\\addlinespace",
  col.names = c("ID", "ECR Forum Feedback"),
  caption =
    sprintf("From the %s people responded to this question", paste(ns, collapse = " completed surveys, ")),
  align = 'cl', 
  longtable = T #break the table over multiple pages
  ) %>%
  column_spec(2, width = "5.5in") %>% 
  kable_styling(full_width = F, 
                latex_options = c("repeat_header", "hold_position")) 
# use different styling to repeat the header


```

\newpage
\captionsetup[table]{labelformat=empty}

## Ideas for the DVC(R) forum with MCRs
What would you like to see in future fora with the DVC(R)?

```{r table for forum ideas}

# use for complete report not report for Rob

# put relevant data in a tibble
forum_ideas <- df %>% 
  dplyr::select(c(id, future_fora)) %>% 
  filter(!future_fora == "NA") %>%  # remove the NA values
  mutate(responses = 1:n()) %>% 
  relocate(responses, .after = id)

# get the relevant ns for the header
total_n <- length(unique(df$id))
resp_n <- length(unique(forum_ideas$id))
ns <- c(total_n, resp_n) 

forum_ideas <- forum_ideas %>% 
  dplyr::select(c(id, future_fora))

knitr::kable (
  forum_ideas,
  booktabs = T,
  linesep = "\\addlinespace",
  col.names = c("ID", "MCR Forum Ideas"),
  caption =
    sprintf("From the %s people responded to this question", paste(ns, collapse = " completed surveys, ")),
  align = 'cl', 
  longtable = T #break the table over multiple pages
  ) %>%
  column_spec(2, width = "5.5in") %>% 
  kable_styling(full_width = F, 
                latex_options = c("repeat_header", "hold_position")) 
# use different styling to repeat the header


```


\captionsetup[table]{labelformat=empty}

## Ideas for other training and development opportunities
What other researcher training and development opportunities would you like to see
at Flinders?

```{r table for other training}

# put relevant data in a tibble
other_training <- df %>% 
  dplyr::select(c(id, training)) %>% 
  filter(!training == "NA") %>%  # remove the NA values
  mutate(responses = 1:n()) %>% 
  relocate(responses, .after = id)

# get the relevant ns for the header
total_n <- length(unique(df$id))
resp_n <- length(unique(other_training$id))
ns <- c(total_n, resp_n) 

other_training <- other_training %>% 
  dplyr::select(c(id, training))

knitr::kable (
  other_training,
  booktabs = T,
  linesep = "\\addlinespace",
  col.names = c("ID", "Other Training Ideas"),
  caption =
    sprintf("From the %s people responded to this question", paste(ns, collapse = " completed surveys, ")),
  align = 'cl', 
  longtable = T #break the table over multiple pages
  ) %>%
  column_spec(2, width = "5.5in") %>% 
  kable_styling(full_width = F, 
                latex_options = c("repeat_header", "hold_position")) 
# use different styling to repeat the header


```

\newpage
\captionsetup[table]{labelformat=empty}

## Communication preferences
How do you prefer to find out about researcher training and development opportunities
(e.g., targeted emails, College newsletters, Research Link weekly newsletter, all of the above)? 


```{r recode comms}

# put relevant data in a tibble (will need this for the table, so do not combine
  # with tibble below)

comms <- df %>% 
  dplyr::select(c(id, comms_preference)) %>% 
  filter(! comms_preference == "NA") %>%  # remove the NA values
  mutate(responses = 1:n()) %>% 
  relocate(responses, .after = id) %>% 
    mutate(length = str_length(comms_preference)) %>% # I could delete these when I'm done playing
  mutate(text_report = case_when (length > 20 ~ "yes", 
                                  TRUE ~ "no"))

# put relevant data in a tibble
comms_recode <- comms %>% 
  mutate(college_newsletter1 = str_detect(comms_preference, regex("College", ignore_case = T))) %>% # one wonky case that needs to be recoded
  mutate(emails = str_detect(comms_preference, regex("email", ignore_case = T))) %>% 
  mutate(researchlink = str_detect(comms_preference, regex("Link", ignore_case = T))) %>% 
  mutate(all = str_detect (comms_preference, regex("all", ignore_case = T))) %>% 
  mutate(college_newsletter = case_when (id == "10" ~ FALSE, 
                                         TRUE ~ (college_newsletter1)))

total_n <- length(comms_recode$id)

# SELECT THE RATING COLUMNS & SAVE AS A TIBBLE I WANT TO SUMMARISE & PLOT USING THE RATING_SUMMARY FUNCTION

comms_options <- comms_recode %>% 
  select (c("college_newsletter", 
            "emails", 
            "researchlink", 
            "all")) 
  
columns <- c("college_newsletter", 
            "emails", 
            "researchlink", 
            "all")

comms_summary <- purrr::map_dfr(columns, .f = function(column) {
	ratings_summary(comms_options, column)
})

# rename the comms options as well as the true and false

comms_summary <- comms_summary %>% 
  mutate(comm_options = case_when(rating_item == "college_newsletter" ~ "College newsletters",
                               rating_item == "emails" ~ "Targeted emails",
                               rating_item == "researchlink" ~ "Research Link",
                               TRUE ~ "All of the above")) %>% 
  mutate(response = case_when(rating == "TRUE" ~ "Mentioned", 
                              TRUE ~ "Not mentioned"))

```


Of the `r total_n` respondents, many of them repeated the options available to them
in the question text. As such, we recoded their responses and we report them in 
the figure below. Several respondents mentioned more than one of the communication
channels. 

```{r plot the comms_summary responses}

# use this to reorder the factor within the ggplot code rather than doing it 
  # in its own code

mention <- c("Not mentioned", "Mentioned")


# plot it [this works & shows all numbers]
ggplot(comms_summary, aes(fill = factor(response, levels = mention), y = percentage, x = comm_options)) +
  geom_bar(position="fill", stat="identity", colour = "black") +
  # add text to show the percentage numbers on the figure for selected responses
  geom_text(aes(y = percentage, x = comm_options, label = percentage), position = position_fill(vjust = 0.5), size = 3) +
  scale_fill_manual(values = c("#d2e2f0", "#2171b5"),
                    labels = c("Not mentioned", "Mentioned"), 
                    guide = guide_legend (reverse = TRUE)) +
  labs (x = element_blank(),
        y = "Percentage") +
  theme_classic() +
theme(legend.title = element_blank()) +
    coord_flip() +
  scale_y_continuous(labels = c("0", "25", "50", "75", "100"))


```

```{r table for comms}

# use the comms tibble

comms2 <- comms %>% 
  mutate(length = str_length(comms_preference)) %>% 
  mutate(text_report = case_when (length > 20 ~ "yes", 
                                  TRUE ~ "no")) 
#  mutate(text_report2 = case_when (id == "4" ~ "no",
#                                 id == "5" ~ "no",
#                                  TRUE ~ text_report))

comms <- comms2 %>% 
  filter (text_report == "yes") %>% 
  dplyr::select(c(id, comms_preference))


knitr::kable (
  comms,
  booktabs = T,
  linesep = "\\addlinespace",
  col.names = c("ID", "Communications preferences"),
  caption =
   sprintf("The responses below provided details beyond those captured in the previous figure"),
  align = 'cl', 
  longtable = T #break the table over multiple pages
  ) %>%
  column_spec(2, width = "5.5in") %>% 
  kable_styling(full_width = F, 
                latex_options = c("repeat_header", "hold_position")) 
# use different styling to repeat the header


```


\newpage
\captionsetup[table]{labelformat=empty}

## Final comments
Is there anything else you would like us to know?

```{r table for anything else}

# put relevant data in a tibble
anything <- df %>% 
  dplyr::select(c(id, anything_else)) %>% 
  filter(!anything_else == "NA") %>%  # remove the NA values
  mutate(responses = 1:n()) %>% 
  relocate(responses, .after = id)

# get the relevant ns for the header
total_n <- length(unique(df$id))
resp_n <- length(unique(anything$id))
ns <- c(total_n, resp_n) 

anything <- anything %>% 
  dplyr::select(c(id, anything_else))

knitr::kable (
  anything,
  booktabs = T,
  linesep = "\\addlinespace",
  col.names = c("ID", "Other Ideas"),
  caption =
   sprintf("From the %s people responded to this question", paste(ns, collapse = " completed surveys, ")),
  align = 'cl', 
  longtable = T #break the table over multiple pages
  ) %>%
  column_spec(2, width = "5.5in") %>% 
  kable_styling(full_width = F, 
                latex_options = c("repeat_header", "hold_position")) 
# use different styling to repeat the header


```

If you have any questions, please contact Dr Jen Beaudry, Manager, Researcher Training, Development and Communication in Research Development and Support. 
