---
title: "DVCR Forum with MCRs (April 2024)"
subtitle: "Summary of Responses to RDS Survey: Complete Report"
#author: "Jen Beaudry"
#date: "11/07/2024"
output: pdf_document
editor_options: 
  chunk_output_type: console
header-includes:
  - \usepackage{caption}
  - \usepackage{titling}
    \setlength{\droptitle}{-2cm} # removes some of the white space above title
  - \pretitle{\begin{center}
    \includegraphics[width=1.5in, height=1.5in]{flinders-university-horizontal-master.png}\LARGE\\} # adds logo
  - \posttitle{\end{center}}
  - \usepackage{fancyhdr}
  - \fancypagestyle{plain}{\pagestyle{fancy}} # sets the footer on page 1
  - \pagestyle{fancy} # sets the footer on page 2 and beyond
  - \fancyhf{} # clears existing header & footer
  - \renewcommand{\headrulewidth}{0pt} # removes the line from the header
  - \fancyfoot[L]{Jen Beaudry} # my name in footer
  - \fancyfoot[R]{\thepage} # page number in foooter
---

```{r setup, include=FALSE}

### NOTE: USE THIS FOR THE FULL REPORT ###

knitr::opts_chunk$set(echo = FALSE,
                      include = TRUE, 
                      eval = TRUE)

# REMEMBER: Until you figure out parameterized reports, you'll have to manually 
  # select which chunks to run and will need to delete the 'empty pages' that 
  # aren't included in Rob's report

```

```{r library, include=FALSE}

library(here)
library(tidyverse)
library(kableExtra)
library(RColorBrewer)

```

```{r functions, include=FALSE}

styler_pdf <- function(dat) {
  dat %>%
     kable_styling(full_width = F, 
                latex_options = c("striped", "HOLD_position"))
}

source(here("..", "functions", "ratings_summary.R"))

```

```{r load data, include=FALSE}

df <- read_csv(here::here("data", "mcr_forum_processed.csv"), lazy = FALSE)

```

We asked our attendees five questions. One was about the forum, two were about
their training and development needs, one was about how they want us to communicate
opportunities to them, and one was an open-ended question giving 
them a chance to tell us anything else they wanted us to know. 

Of the 19 mid-career researchers who attended this session, `r nrow(df)` 
completed the survey. 

\captionsetup[table]{labelformat=empty}

## Ideas for the DVC(R) forum with ECRs
What would you like to see in future fora with the DVC(R)?

```{r table for forum ideas}

# use for complete report not report for Rob

# put relevant data in a tibble
forum_ideas <- df %>% 
  dplyr::select(c(id, future_fora)) %>% 
  filter(!future_fora == "NA") %>%  # remove the NA values
  mutate(responses = 1:n()) %>% 
  relocate(responses, .after = id)

# get the relevant ns for the header
total_n <- length(unique(df$id))
resp_n <- length(unique(forum_ideas$id))
ns <- c(total_n, resp_n) 

forum_ideas <- forum_ideas %>% 
  dplyr::select(c(id, future_fora))

knitr::kable (
  forum_ideas,
  booktabs = T,
  linesep = "\\addlinespace",
  col.names = c("ID", "MCR Forum Ideas"),
  caption =
    sprintf("From the %s people responded to this question", paste(ns, collapse = " completed surveys, ")),
  align = 'cl', 
  longtable = T #break the table over multiple pages
  ) %>%
  column_spec(2, width = "5in") %>% 
  kable_styling(full_width = F, 
                latex_options = c("repeat_header", "hold_position")) 
# use different styling to repeat the header


```


\newpage
## Interest in potential training and development topics
We are considering expanding our training and development offerings in the future.
From the `r nrow(df)` respondents, their interest in attending the various topics 
is illustrated below.

\vskip 0.3in

```{r creating tibbles for all training responses, include=FALSE}

# breadcrumb: I think I now have a function for this, so I can probably simplify this code. 

# get total n to calculate percentages

total_n <- length(unique(df$id))

# create tibbles for each training option so I can create stacked bar charts

os <- df %>% 
  mutate(response = open_science, .keep = "unused") %>% 
  dplyr::count(response) %>% 
  mutate(training = "Open science", .before = response) %>% 
  mutate(percentage = round (n/(total_n)*100))


ldr <- df %>% 
  mutate(response = leadership, .keep = "unused") %>% 
  dplyr::count(response) %>% 
  mutate(training = "Leadership skills", .before = response) %>% 
  mutate(percentage = round (n/(total_n)*100))


prod <- df %>% 
  mutate(response = productivity, .keep = "unused") %>% 
  dplyr::count(response) %>% 
  mutate(training = "Research productivity", .before = response) %>% 
  mutate(percentage = round (n/(total_n)*100))

e_i <- df %>% 
  mutate(response = engagement_impact, .keep = "unused") %>% 
  dplyr::count(response) %>% 
  mutate(training = "Engagement and impact", .before = response) %>% 
  mutate(percentage = round (n/(total_n)*100))

well <- df %>% 
  mutate(response = wellbeing, .keep = "unused") %>% 
  dplyr::count(response) %>% 
  mutate(training = "Well-being issues", .before = response) %>% 
  mutate(percentage = round (n/(total_n)*100))

pitch <- df %>% 
  mutate(response = pitch_research, .keep = "unused") %>% 
  dplyr::count(response) %>% 
  mutate(training = "Pitching research", .before = response) %>% 
  mutate(percentage = round (n/(total_n)*100))

grant <- df %>% 
  mutate(response = grantsmanship, .keep = "unused") %>% 
  dplyr::count(response) %>% 
  mutate(training = "Grantsmanship", .before = response) %>% 
  mutate(percentage = round (n/(total_n)*100))

plan <- df %>% 
  mutate(response = career_planning, .keep = "unused") %>% 
  dplyr::count(response) %>% 
  mutate(training = "Career planning", .before = response) %>% 
  mutate(percentage = round (n/(total_n)*100))

pm <- df %>% 
  mutate(response = project_management, .keep = "unused") %>% 
  dplyr::count(response) %>% 
  mutate(training = "Project management", .before = response) %>% 
  mutate(percentage = round (n/(total_n)*100))

# join the tibbles

train <- os %>% 
  full_join(ldr) %>% 
  full_join(prod) %>% 
  full_join(e_i) %>% 
  full_join(well) %>%
  full_join(pitch) %>% 
  full_join(grant) %>% 
  full_join(plan) %>% 
  full_join(pm)

```

```{r plot the training responses}

# rename NAs
train[is.na(train)] <- "No response"

# use this to reorder the factor within the ggplot code rather than doing it 
  # in its own code
attend <- c("No response", "I would not attend", "I might attend", "I would attend")


# create a label variable so that only certain responses have labels
train <- train %>% 
  mutate(my_label = case_when (response == "I would attend" ~ "yes",
                               response == "I might attend" ~"yes",
                               TRUE ~ "no"))


# plot it [this works & shows certain numbers]
  # I am not using brewer because I want NA to be at the bottom of the legend, so I need to manually control things
ggplot(train, aes(fill = factor(response, levels = attend), y = percentage, x = training)) +
  geom_bar(position="fill", stat="identity", colour = "black") +
  # add text to show the percentage numbers on the figure for selected responses
  geom_text(aes(y = percentage, x = training, label = ifelse(my_label=="yes", percentage, "")), position = position_fill(vjust = 0.5), size = 3) +
  scale_fill_manual(values = c("#bfbfbf", "#d2e2f0", "#90b8da", "#377fbc"),
                    labels = c("No response", "I would not attend", "I might attend", "I would attend"), 
                    guide = guide_legend (reverse = TRUE)) +
  labs (x = element_blank(),
        y = "Percentage") +
  theme_classic() +
theme(legend.title = element_blank()) +
    coord_flip() +
  scale_y_continuous(labels = c("0", "25", "50", "75", "100"))

```

\newpage
\captionsetup[table]{labelformat=empty}

## Ideas for other training and development opportunities
What other researcher training and development opportunities would you like to see
at Flinders?

```{r table for other training}

# put relevant data in a tibble
other_training <- df %>% 
  dplyr::select(c(id, other_opportunities)) %>% 
  filter(!other_opportunities == "NA") %>%  # remove the NA values
  mutate(responses = 1:n()) %>% 
  relocate(responses, .after = id)

# get the relevant ns for the header
total_n <- length(unique(df$id))
resp_n <- length(unique(other_training$id))
ns <- c(total_n, resp_n) 

other_training <- other_training %>% 
  dplyr::select(c(id, other_opportunities))

knitr::kable (
  other_training,
  booktabs = T,
  linesep = "\\addlinespace",
  col.names = c("ID", "Other Training Ideas"),
  caption =
    sprintf("From the %s people responded to this question", paste(ns, collapse = " completed surveys, ")),
  align = 'cl', 
  longtable = T #break the table over multiple pages
  ) %>%
  column_spec(2, width = "5in") %>% 
  kable_styling(full_width = F, 
                latex_options = c("repeat_header", "hold_position")) 
# use different styling to repeat the header


```


\newpage
\captionsetup[table]{labelformat=empty}

## Communication preferences
How do you prefer to find out about researcher training and development opportunities
(e.g., targeted emails, College newsletters, Research Link weekly newsletter, all of the above)? 


```{r recode comms}

# put relevant data in a tibble (will need this for the table, so do not combine
  # with tibble below)

comms <- df %>% 
  dplyr::select(c(id, comms_preference)) %>% 
  filter(! comms_preference == "NA") %>%  # remove the NA values
  mutate(responses = 1:n()) %>% 
  relocate(responses, .after = id) %>% 
    mutate(length = str_length(comms_preference)) %>% # I could delete these when I'm done playing
  mutate(text_report = case_when (length > 20 ~ "yes", 
                                  TRUE ~ "no"))

# put relevant data in a tibble
comms_recode <- comms %>% 
  mutate(college_newsletter1 = str_detect(comms_preference, regex("College", ignore_case = T))) %>% # one wonky case that needs to be recoded
  mutate(emails = str_detect(comms_preference, regex("email", ignore_case = T))) %>% 
  mutate(researchlink = str_detect(comms_preference, regex("Link", ignore_case = T))) %>% 
  mutate(all = str_detect (comms_preference, regex("all", ignore_case = T))) %>% 
  mutate(college_newsletter = case_when (id == "10" ~ FALSE, 
                                         TRUE ~ (college_newsletter1)))

total_n <- length(comms_recode$id)

# SELECT THE RATING COLUMNS & SAVE AS A TIBBLE I WANT TO SUMMARISE & PLOT USING THE RATING_SUMMARY FUNCTION

comms_options <- comms_recode %>% 
  select (c("college_newsletter", 
            "emails", 
            "researchlink", 
            "all")) 
  
columns <- c("college_newsletter", 
            "emails", 
            "researchlink", 
            "all")

comms_summary <- purrr::map_dfr(columns, .f = function(column) {
	ratings_summary(comms_options, column)
})

# rename the comms options as well as the true and false

comms_summary <- comms_summary %>% 
  mutate(comm_options = case_when(rating_item == "college_newsletter" ~ "College newsletters",
                               rating_item == "emails" ~ "Targeted emails",
                               rating_item == "researchlink" ~ "Research Link",
                               TRUE ~ "All of the above")) %>% 
  mutate(response = case_when(rating == "TRUE" ~ "Mentioned", 
                              TRUE ~ "Not mentioned"))

```


Of the `r total_n` respondents, many of them repeated the options available to them
in the question text. As such, we recoded their responses and we report them in 
the figure below. Several respondents mentioned more than one of the communication
channels. 

```{r plot the comms_summary responses}

# use this to reorder the factor within the ggplot code rather than doing it 
  # in its own code

mention <- c("Not mentioned", "Mentioned")


# plot it [this works & shows all numbers]
ggplot(comms_summary, aes(fill = factor(response, levels = mention), y = percentage, x = comm_options)) +
  geom_bar(position="fill", stat="identity", colour = "black") +
  # add text to show the percentage numbers on the figure for selected responses
  geom_text(aes(y = percentage, x = comm_options, label = percentage), position = position_fill(vjust = 0.5), size = 3) +
  scale_fill_manual(values = c("#d2e2f0", "#2171b5"),
                    labels = c("Not mentioned", "Mentioned"), 
                    guide = guide_legend (reverse = TRUE)) +
  labs (x = element_blank(),
        y = "Percentage") +
  theme_classic() +
theme(legend.title = element_blank()) +
    coord_flip() +
  scale_y_continuous(labels = c("0", "25", "50", "75", "100"))


```

```{r table for comms}

# use the comms tibble

comms2 <- comms %>% 
  mutate(length = str_length(comms_preference)) %>% 
  mutate(text_report = case_when (length > 20 ~ "yes", 
                                  TRUE ~ "no")) %>% 
  mutate(text_report2 = case_when (id == "4" ~ "no",
                                  id == "5" ~ "no",
                                  TRUE ~ text_report))

comms <- comms2 %>% 
  filter (text_report2 == "yes") %>% 
  dplyr::select(c(id, comms_preference))


knitr::kable (
  comms,
  booktabs = T,
  linesep = "\\addlinespace",
  col.names = c("ID", "Communications preferences"),
  caption =
   sprintf("The responses below provided details beyond those captured in the previous figure"),
  align = 'cl', 
  longtable = T #break the table over multiple pages
  ) %>%
  column_spec(2, width = "5in") %>% 
  kable_styling(full_width = F, 
                latex_options = c("repeat_header", "hold_position")) 
# use different styling to repeat the header


```


\newpage
\captionsetup[table]{labelformat=empty}

## Final comments
Is there anything else you would like us to know?

```{r table for anything else}

# put relevant data in a tibble
anything <- df %>% 
  dplyr::select(c(id, anything_else)) %>% 
  filter(!anything_else == "NA") %>%  # remove the NA values
  mutate(responses = 1:n()) %>% 
  relocate(responses, .after = id)

# get the relevant ns for the header
total_n <- length(unique(df$id))
resp_n <- length(unique(anything$id))
ns <- c(total_n, resp_n) 

anything <- anything %>% 
  dplyr::select(c(id, anything_else))

knitr::kable (
  anything,
  booktabs = T,
  linesep = "\\addlinespace",
  col.names = c("ID", "Other Ideas"),
  caption =
   sprintf("From the %s people responded to this question", paste(ns, collapse = " completed surveys, ")),
  align = 'cl', 
  longtable = T #break the table over multiple pages
  ) %>%
  column_spec(2, width = "5in") %>% 
  kable_styling(full_width = F, 
                latex_options = c("repeat_header", "hold_position")) 
# use different styling to repeat the header


```


